UKB Simulation Analyses

### 2023-12-11 ukb_sim.site_analyses.Rmd
adding data dist. plots

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
source("./cubic_scripts/R_scripts/ranked_welch_tests.R")
# 
# # Enable this universe
# options(repos = c(
#   ggseg = 'https://ggseg.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# 
# # Install some packages
# install.packages('ggsegExtra')
```

@@

@@

  #group-wise
  df.aov <- tidy(kruskal.test(cent.diffs2[[pheno]] ~ cent.diffs2[["dataset"]]))
  df.aov$pheno <- pheno
  sum.df <- rbind(sum.df, df.aov)

>>>>

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
source("./cubic_scripts/R_scripts/ranked_welch_tests.R")
source("/Users/megardn/Desktop/BGD_Repos/GAMLSS/plotting_functions.R")
# 
# # Enable this universe
# options(repos = c(
#   ggseg = 'https://ggseg.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# 
# # Install some packages
# install.packages('ggsegExtra')
```

@@

## Plot Centiles

```{r}
#load data csvs
ukb_df_cf.gam <- fread(file="data/ukb_to_model/cf.gam_data.csv")
ukb_df_cf.gamlss <- fread(file="data/ukb_to_model/cf.gamlss_data.csv")
ukb_df_cf.lm <- fread(file="data/ukb_to_model/cf.lm_data.csv")
```

plot data distributions (not loading models for now)
```{r}
ven_raw <- ggplot(ukb_df_age.filt) +
  geom_point(aes(x=log_age, y=Ventricles, color=sex), alpha =0.3) +
  ggtitle("Raw Data")

ven_lm <- ggplot(ukb_df_cf.lm) +
  geom_point(aes(x=log_age, y=Ventricles, color=sex), alpha =0.3) +
  ggtitle("ComBat")

ven_gam <- ggplot(ukb_df_cf.gam) +
  geom_point(aes(x=log_age, y=Ventricles, color=sex), alpha =0.3) +
  ggtitle("ComBat-GAM")

ven_gamlss <- ggplot(ukb_df_cf.gamlss) +
  geom_point(aes(x=log_age, y=Ventricles, color=sex), alpha =0.3) +
  ggtitle("ComBatLS")

ggarrange(ven_raw, ven_lm, ven_gam, ven_gamlss, ncol=2, nrow=2, common.legend=TRUE)
```

```{r}
rh_CT_bankssts_raw <- ggplot(ukb_df_age.filt) +
  geom_point(aes(x=log_age, y=rh_CT_bankssts, color=sex), alpha =0.3) +
  ggtitle("Raw Data")

rh_CT_bankssts_lm <- ggplot(ukb_df_cf.lm) +
  geom_point(aes(x=log_age, y=rh_CT_bankssts, color=sex), alpha =0.3) +
  ggtitle("ComBat")

rh_CT_bankssts_gam <- ggplot(ukb_df_cf.gam) +
  geom_point(aes(x=log_age, y=rh_CT_bankssts, color=sex), alpha =0.3) +
  ggtitle("ComBat-GAM")

rh_CT_bankssts_gamlss <- ggplot(ukb_df_cf.gamlss) +
  geom_point(aes(x=log_age, y=rh_CT_bankssts, color=sex), alpha =0.3) +
  ggtitle("ComBatLS")

ggarrange(rh_CT_bankssts_raw, rh_CT_bankssts_lm, rh_CT_bankssts_gam, rh_CT_bankssts_gamlss, ncol=2, nrow=2, common.legend=TRUE)
```

@@

  #group-wise
  df.aov <- tidy(kruskal.test(cent.diffs2[[pheno]] ~ cent.diffs2[["dataset"]])) #nonparametric b/c distribution but also data is paired? ask andrews
  df.aov$pheno <- pheno
  sum.df <- rbind(sum.df, df.aov)
